### 2024-08-15 README.Rmd
update README to fit the tidy formatting
Deleted backticks from the packages' names and added commas after i.e.

The objective of this package is to perform statistical inference using an expressive statistical grammar that coheres with the `tidyverse` design framework. The package is centered around 4 main verbs, supplemented with many utilities to visualize and extract value from their outputs.

@@

To install the current stable version of `infer` from CRAN:

@@

To install the developmental stable version of `infer`, make sure to install `remotes` first. The `pkgdown` website for this version is at [infer.tidymodels.org](https://infer.tidymodels.org/).

@@

Note that the formula and non-formula interfaces  (i.e. `age ~ partyid` vs. `response = age, explanatory =  partyid`) work for all implemented inference procedures in `infer`. Use whatever is more natural for you. If you will be doing modeling using functions like `lm()` and `glm()`, though, we recommend you begin to use the formula `y ~ x` notation as soon as possible.

>>>>

The objective of this package is to perform statistical inference using an expressive statistical grammar that coheres with the tidyverse design framework. The package is centered around 4 main verbs, supplemented with many utilities to visualize and extract value from their outputs.

@@

To install the current stable version of infer from CRAN:

@@

To install the developmental stable version of infer, make sure to install remotes first. The `pkgdown` website for this version is at [infer.tidymodels.org](https://infer.tidymodels.org/).

@@

Note that the formula and non-formula interfaces  (i.e., `age ~ partyid` vs. `response = age, explanatory =  partyid`) work for all implemented inference procedures in `infer`. Use whatever is more natural for you. If you will be doing modeling using functions like `lm()` and `glm()`, though, we recommend you begin to use the formula `y ~ x` notation as soon as possible.
